---
title: "Tabular Playground - Feb. 2021"
author: "Brad Hill"
date: "2/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Intro  

What are we doing here? This [project](https://www.kaggle.com/c/tabular-playground-series-feb-2021/overview) is kind of an intro to Kaggle project that rewards top submissions with Kaggle merch. I don't know what I'm doing, but I want merch. So let's load some libraries and read data in.

### Load Libraries
```{r message = F}
library(tidyverse)
library(here)
library(rsample)
library(kknn)
library(GGally)
library(prcomp)
```

```{r cache=T, message = F}
train <- read_csv(here('tabular_playground_feb21/data/train.csv'))
```

```{r echo=F}
train[1:5, c(1:4, 20:23, 26)] %>% 
  knitr::kable()
```

All categorical variables start with `cat`, all continuous variables start with `cont`, and our response variable lives in `target`. We have a variable called `id` that we want to make sure we don't include in any models because it doesn't actually mean anything.   
  
We're also going to want to do cross-validation on this since we already have a test set. Let's use `rsample` to create a cross-validation object, using 10 folds.

```{r}
train_cv <- vfold_cv(train, v = 10)
```


```{r}
train %>% 
  mutate(across(where(is.character), as.factor)) %>% 
  summary()
```

```{r echo = F}
train %>% 
  mutate(across(where(is.character), as.factor)) %>%
  sample_n(200) %>% 
  select(starts_with('cat'), target) %>% 
  pivot_longer(cols = c(-target)) %>% 
  ggplot() +
  geom_boxplot(aes(value, target)) +
  facet_wrap(~name, scales = 'free')
```

```{r echo=F}
train %>% 
  mutate(across(where(is.character), as.factor)) %>%
  sample_n(200) %>% 
  select(starts_with('cont'), target) %>% 
  pivot_longer(cols = c(-target)) %>% 
  ggplot() +
  geom_histogram(aes(value)) +
  facet_wrap(~name, scales = 'free')
```

